---
title: "Regression solution"
author: "Volodymyr Mikhieiev"
date: "17 05 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This is assignment is inspired by practices of [Ryan Miller] (https://remiller1450.github.io/).

## Using regression for predicting binary outcome.

The [Donner Party] (https://en.wikipedia.org/wiki/Donner_Party) dataset documents the fate of members of the Donner Party, a group of 45 pioneers whose migration to California was delayed by a series of mishaps which resulted in the group being stranded in the Sierra Nevada mountains.

**Problem**
Predict survival status members of the Donner Party. The target variable is `Survived`.

## Task

Read the data. Pay attention that data has NA values. It's better to convert target variable to factor.
```{r}
data <- read.csv("./lab3_data/donner_party.csv", sep=",", stringsAsFactors = TRUE)
data <- na.omit(data)
data$Survived <- as.factor(data$Survived)
```

For prediction we will use only variables `Sex` and `Age`. 

For predicting binary outcome we will use **Generalized Linear Model** (`method = "glm"`) and **caret package**. 

```{r}
library(caret)
formula <- Survived ~ Sex + Age
model = train(formula, data = data, method = 'glm', family = 'binomial')
predicted_data <- predict(model, newdata = data)
```

What is your in-sample accuracy? Build a confusion matrix

```{r}
confusionMatrix(predicted_data, data$Survived)
```

Use a cross-validation with `method = "repeatedcv"`, `number = 5`, `repeats = 10`. Does cross-validation improve the accuracy?

```{r}
train_control = trainControl(method = "repeatedcv", number = 5, repeats = 10)
modelNew = train(formula, data = data, method = 'glm', family = 'binomial', trControl = train_control)
predicted_data_new <- predict(modelNew, newdata = data)
confusionMatrix(predicted_data_new, data$Survived)
```

Answer: Accuracy remained the same. Cross-validation did not improve it.
